\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\Huge \scshape SANDEEP SINGH} \\ \vspace{2pt}
    %% >>>TAILOR:subtitle (scripts/tailor.mjs replaces this line per JD; safe to edit)
    {\large AI Engineer $|$ Agent Infrastructure \& LLM Systems $|$ Full-Stack Engineer} \\ \vspace{4pt}
    %% <<<TAILOR:subtitle
    \small
    \href{mailto:sandy1711003@gmail.com}{\underline{sandy1711003@gmail.com}} \,$\bullet$\,
    \href{https://linkedin.com/in/sandeep-singh-445058254/}{\underline{linkedin.com/in/sandeep-singh-445058254}} \,$\bullet$\,
    \href{https://github.com/Sandy-1711}{\underline{github.com/Sandy-1711}} \,$\bullet$\,
    +91 8953596712
    \\[6pt]
    %% >>>TAILOR:summary (scripts/tailor.mjs replaces this line per JD; safe to edit)
   \textbf{AI Engineer} building agentic LLM systems, memory, and RAG --- \textbf{12 merged PRs} into Mastra's agent runtime (\textbf{25k+ stars}), shipped production agents at AiRA, and scaled a campus platform to \textbf{10,000+ users}.
    %% <<<TAILOR:summary
    \vspace{-8pt}
\end{center}

\section{Experience}
  \resumeSubHeadingListStart

\resumeSubheading
  {AiRA}{Nov 2025 - March 2026}
  {AI Engineer (Agent Orchestration, Memory, RAG \& Systems)}{Bangalore, India}
  \resumeItemListStart
    \resumeItem{Built the flagship \textbf{Daily Brief} agent (\textbf{Python}/\textbf{FastAPI}) --- an \textbf{agentic orchestration loop} coordinating Email, Calendar, and \textbf{Exa AI} web-search tools via \textbf{asyncio} to deliver each user a personalized morning briefing of priority emails, events, and news.}

    \resumeItem{Designed a self-maintaining \textbf{Canvas} agent generating persistent, per-user web apps and documents, with automatic \textbf{versioning and data-shape migration} that keeps prior user data compatible across regenerations.}

    \resumeItem{Architected a multi-tier \textbf{memory system} (working / medium / long-term) on \textbf{MongoDB} and \textbf{Redis} that summarizes each user's conversations and style into a preferences store for personalization and proactive check-ins.}

    \resumeItem{Built an \textbf{LLM evaluation} pipeline with \textbf{promptfoo}, benchmarking 8+ models (Anthropic, OpenAI, Grok) on tool-calling accuracy, memory use, and latency to standardize model selection.}

    \resumeItem{Cut routing-\textbf{LLM} token usage by \textbf{82\%} via artifact-based generalized prompting and context deduplication across 3 core prompts, and parallelized the Orchestrator's tool-calling to reduce execution latency.}

    \resumeItem{Implemented \textbf{Langfuse} observability for LLM traces, latency, and cost, cutting time-to-debug for agent failures in production.}
  \resumeItemListEnd

    \resumeSubheading
      {IIT Kharagpur}{May 2025 - Aug 2025}
      {Research Intern (Multimodal AI)}{Kharagpur, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{CircuitSynth}, a multimodal reasoning framework, fine-tuning \textbf{Qwen models (4B/8B)} with \textbf{LoRA/QLoRA} to generate executable Arduino circuit JSONs.}
        \resumeItem{Achieved \textbf{75\% accuracy} on complex circuit-generation tasks (vs. near-zero for general-purpose GPT models) via a multi-stage \textbf{RAG} pipeline with automated unit-style validation.}
        \resumeItem{Optimized inference for edge deployment, running quantized \textbf{GGUF} models on \textbf{Raspberry Pi} devices.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-12pt}

\section{Projects}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{Samagra} --- Founding Software Engineer, Indigle \, \href{https://play.google.com/store/apps/details?id=com.indigle.samagra}{\underline{Play Store}}}{Sep 2024 - Sep 2025}
          \resumeItemListStart
            \resumeItem{Built \textbf{Samagra}, a full-stack campus ERP platform grown to \textbf{10,000+ active users}, spanning a \textbf{React Native} mobile client, a \textbf{Node.js}/\textbf{Express} \textbf{REST API}, \textbf{MongoDB}, and a \textbf{Next.js} web app.}
            \resumeItem{Engineered \textbf{JWT authentication} with \textbf{role-based access control}, rate limiting, and \textbf{Socket.io} real-time sync across the platform, sustaining \textbf{99.9\% uptime}.}
            \resumeItem{Owned the product end-to-end --- architecture, \textbf{CI/CD}, release, and Play Store distribution --- on a \textbf{zero-cost} Vercel-hosted backend handling \textbf{150k+ monthly API requests} at sub-100ms latency.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Open Source} $|$ \emph{TypeScript, Node.js, React, Vue.js}}{2025 - Present}
          \resumeItemListStart
            \resumeItem{\textbf{mastra-ai/mastra (25k+ stars)} \href{https://github.com/mastra-ai/mastra/pulls?q=author:Sandy-1711}{\underline{[PR list]}}: \textbf{12 merged PRs} across the core agent runtime, streaming, ai-sdk, and Studio --- including fixes to \textbf{semantic recall} injection, duplicate \textbf{stream-event delivery} on observe/replay, and tool-level \textbf{background execution} config. Active contributor since June 2026.}
            \resumeItem{\textbf{cal.com (46k+ stars)}: Authored a full \textbf{BigBlueButton video integration} (checksum-signed client, encrypted credential storage) plus a generalized install-router fix for non-OAuth apps --- \textbf{912 LOC, 32 unit tests} (bounty issue).}
            \resumeItem{\textbf{n8n (195k+ stars)}: Authored core infrastructure fixes --- a Webhook CSP security bug (\texttt{allow-same-origin}) and a cross-platform build-path failure.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd
\vspace{-12pt}

\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     %% >>>TAILOR:skills (scripts/tailor.mjs may reorder these per JD; safe to edit)
     \textbf{AI/ML \& LLM}{: Hugging Face (PEFT/LoRA), LangChain, Langfuse, LlamaIndex, Mastra, OpenAI/Gemini API, Pinecone, promptfoo, Python (Expert), PyTorch, Qdrant} \\
     \textbf{Backend \& Ops}{: asyncio, AWS (Lambda, S3), CI/CD (GitHub Actions), Docker, FastAPI, MongoDB, PostgreSQL, Redis, REST APIs, WebSockets} \\
     \textbf{Frontend \& Mobile}{: Next.js, React Native (Expo), React.js, Shadcn/UI, Tailwind CSS} \\
     \textbf{Languages}{: JavaScript, Python, SQL, TypeScript}
     %% <<<TAILOR:skills
    }}
 \end{itemize}
 \vspace{-12pt}

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Madan Mohan Malviya University of Technology}{Nov 2022 -- Aug 2026}
      {B.Tech in Electronics \& Communication Engineering (CGPA: 7.32)}{Gorakhpur, India}
  \resumeSubHeadingListEnd

\end{document}